Fast and optimal centroiding of faint stars

### 2014-12-16 ms/figure.tex
abstract updates

\begin{abstract}

We present a modification of the 3$\times$3 polynomial method for estimating the centroid 
of stars in astronomical images. After simulating a large number of stars with relatively low 
signal-to-noise-ratio, and in a wide range of full width at half maxima, we compare the results
of our method to those obtained from the quartic approximation method used in SDSS photometric pipeline, 
as well as finding the centroid by fitting the exact PSF model which was used to generate the 
simulated data. Comparison of the root-mean-squared error in centroid measurement, resulting 
from these techniques to the Cramer-Rao lower bound of centroid estimates, 
suggests that, the modified 3$\times$3 polynomial trick, though not as accurate as PSF fitting method
, is able to deliver results sufficiently close to the Cramer-Rao lower bound.

\end{abstract}

>>>>

\begin{abstract}
One of the most demanding tasks in astronomical image processing---in terms of precision---is the centroiding of stars. 
Upcoming large surveys are going to take images of billions of point sources, 
including many faint stars, with short exposure times. Real-time estimation of the
centroid of stars is crucial for real-time PSF estimation, and precision is required
for measurements of proper motion. In this work, we aim to compare the performance of
fast and slow centroiding methods, when they are applied
to relatively low signal-to-noise ratio stars in a wide range of psf sizes.
In order to investigate how information-preserving these techniques are, we compare
the root-mean-squared-error arising from these centroiding methods with the fundamental Cramer-Rao
lower bound. The methods we discuss in this paper include weighted moments, naive 3$\times$3 polynomial centroiding,
the 3$\times$3 quartic approximation used in the \textsl{Sloan Digital Sky Surveys}, and PSF profile fitting
(with both the correct and the incorrect PSF).
We recommend a particular form of polynomial cetroiding; it is very fast.
Although it is not as accurate as PSF profile fitting with a good PSF estimate,
it comes close to saturating the Cramer-Rao lower bound in a wide range of conditions.
\end{abstract}
